---
title: "Curriculum Vitae"
author: "Guillaume Guénard"
date: 'Compiled: `r format(Sys.time(), "%Y-%m-%d")`'
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(yaml)
library(magrittr)

enumerate <- function(x, and = " & ") {
  if(length(x) == 1L) {
    x
  } else {
    y <- rep("", length(x))
    y[length(y) - 1L] <- and
    if(length(y) > 2L) y[1L:(length(y)-2L)] <- ", "
    paste(paste(x,y,sep=""),collapse="")
  }
}

lang <- "en"

"../CVcontents.yml" %>%
  yaml.load_file -> contents
```

```{r, echo = FALSE, results='asis'}
contents$contact[[lang]] %>%
  cat("**Contact:** ",.,"\n",sep="")

contents$links %>%
  lapply(
    function(x)
      paste("[",x$label,"](",x$url,")\n\n",sep="") %>% cat
  ) %>% invisible
```

---

## Interests

```{r, echo = FALSE, results='asis'}
contents$interests %>%
  lapply(
    function(x, lang)
      x[[lang]] %>% paste("-",.) %>% paste(collapse="\n\n") %>% cat,
    lang = lang
  ) %>% invisible
```

---

## Work experience

```{r, echo = FALSE, results='asis'}
contents$experience %>%
  lapply(
    function(x, lang) {
      cat(
        x$position[[lang]],
        " [",x$date,"]\n: ",
        x$place[[lang]],"-- ",
        x$work[[lang]],"-- Supervisor(s): ",
        x$supervisor,
        "\n\n",
        sep=""
      )
    },
    lang = lang
  ) %>% invisible
```

---

## Education

```{r, echo = FALSE, results='asis'}
contents$education %>%
  lapply(
    function(x, lang) {
      cat(
        x$ending, " --- ", x$degree[[lang]], "\n: ",
        x$institution," ",
        if(!is.null(x$description[[lang]])) paste(" -- ", x$description[[lang]]),
        if(!is.null(x$director)) paste(" Director: ", x$director),
        "\n\n",
        sep=""
      )
    },
    lang = lang
  ) %>% invisible
```

---

## Achievements (see the last section for exhaustive listings)

```{r, echo = FALSE, results='asis'}
contents$achievement$prja %>%
  lapply(function(x) x$authors[1L]) %>%
  unlist -> fauth

contents$achievement$prja %>%
  lapply(function(x) x$authors) %>%
  unlist %>% unique %>% sort -> alist

contents$achievement$prja %>%
  lapply(function(x) x$outlet) %>%
  unlist %>% unique %>% sort -> jlist

contents$achievement$presentation  %>%
  lapply(function(x) x$event) %>%
  unlist %>% unique %>% sort -> plist

contents$achievement$presentation %>%
  lapply(function(x) x$authors[1L]) %>%
  unlist -> fpauth

contents$achievement$presentation %>%
  lapply(function(x) x$authors) %>%
  unlist %>% unique %>% sort -> aplist

contents$achievement$report  %>%
  lapply(function(x, lang) x$series[[lang]], lang=lang) %>%
  unlist %>% unique %>% sort -> prlist

contents$achievement$software  %>%
  lapply(function(x) x$name) %>% unlist -> pkgname

contents$achievement$software  %>%
  lapply(function(x) x$maintainer) %>% unlist -> pkgmain
```

Articles
: Publication of **`r length(contents$achievement$prja)`** articles
(**`r sum(fauth == "Guénard, G.")`** as a first author) in
**`r length(jlist)`** peer-reviewed scientific journals: 
`r enumerate(jlist, and = ", and ")`; with contributions from a total of
**`r length(alist) - 1L`** fellow scientists.

Presentations
: **`r length(contents$achievement$presentation)`** authored conference
presentations (in English and French; **`r sum(fpauth == "Guénard, G.")`** as
the speaker) in **`r length(plist)`** national and international symposia:
`r enumerate(plist, and = ", and ")`; with contributions
from a total of **`r length(aplist) - 1L`** fellow scientists.

Research report
: **`r length(contents$achievement$report)`** research reports published
by different institutions and outlets (`r enumerate(prlist, and = ", and ")`).

Software
: contribution in **`r length(contents$achievement$software)`** R language
packages; maintainer for **`r sum(pkgmain)`** of them
(`r enumerate(pkgname[pkgmain], and = ", and ")`).

---

## Awards

```{r, echo = FALSE, results='asis'}
contents$award %>%
  lapply(
    function(x, lang) {
      cat(
        x$name[[lang]]," (",x$date,"; ",x$amount,")",
        "\n\n",
        sep=""
      )
    },
    lang = lang
  ) %>% invisible
```

---

## Teaching experience

```{r, echo = FALSE, results='asis'}
contents$teaching %>%
  lapply(
    function(x, lang) {
      cat(
        "**", x$date, "** ", x$assignment[[lang]], " -- ",
        x$place[[lang]], " _", x$task[[lang]], "_ ",
        if(!is.null(x$supervisor)) paste("Supervisor(s): ", x$supervisor),
        "\n\n",
        sep=""
      )
    },
    lang = lang
  ) %>% invisible
## contents$teaching[[1L]] -> x
```

---

## Professional activities, qualifications, and services

```{r, echo = FALSE, results='asis'}
contents$paqs %>%
  lapply(
    function(x, lang)
      x[[lang]] %>% paste("-",.) %>% paste(collapse="\n\n") %>% cat,
    lang = lang
  ) %>% invisible
```

---

\newpage

# List of achievements

## Peer-reviewed journal articles

```{r, echo = FALSE, results='asis'}
contents$achievement$prja %>%
  lapply(
    function(x) {
      cat(
        "- ",
        enumerate(x$authors), " ",
        x$year,". _",
        x$title,"_ ",
        x$outlet," ",
        x$number,"(",x$issue,")",
        if(!is.null(x$page)) paste(":",x$page) else " ",
        " doi: [",x$doi,"](https://doi.org/",x$doi,")",
        "\n\n",
        sep=""
      )
    }
  ) %>% invisible
```

---

## Authored conference presentations

```{r, echo = FALSE, results='asis'}
contents$achievement$presentation %>%
  lapply(
    function(x, lang) {
      cat(
        "- ",
        enumerate(x$authors), " ",
        x$year,". _",
        x$title,"_ ",
        x$event," -- ",
        x$place[[lang]],
        "\n\n",
        sep=""
      )
    },
    lang = lang
  ) %>% invisible
```

---

## Research reports

```{r, echo = FALSE, results='asis'}
contents$achievement$report %>%
  lapply(
    function(x, lang) {
      cat(
        "- ",
        enumerate(x$authors), " ",
        x$year,". ",
        x$title[[lang]]," ", x$series[[lang]], ". ",
        if(!is.null(x$number)) paste(" ", x$number, ". ", sep="") else ". ",
        x$place[[lang]], ". ",
        x$page, if(!is.null(x$url)) " [LINK](",x$url,")",
        "\n\n",
        sep=""
      )
    },
    lang = lang
  ) %>% invisible
## contents$achievement$report[[2L]] -> x
```

---

## Software packages

```{r, echo = FALSE, results='asis'}
contents$achievement$software %>%
  lapply(
    function(x, lang) {
      cat(
        "[",x$name,"](",x$url,")\n: ",
        enumerate(x$authors), " ",
        x$year,". ",
        x$title," Description: ", x$description, " ", x$version,
        "\n\n",
        sep=""
      )
    },
    lang = lang
  ) %>% invisible
```

---

## Work in progress

```{r, echo = FALSE, results='asis'}
contents$anticipated %>%
  lapply(
    function(x, lang) {
      cat(
        "- ", enumerate(x$authors), " _",
        x$title, "_ [",x$type,"]",
        "\n\n",
        sep=""
      )
    },
    lang = lang
  ) %>% invisible
```

---
